%-------------------------------------------------------------------------------
% seq64_references
%-------------------------------------------------------------------------------
%
% \file        seq64_references.tex
% \library     Documents
% \author      Chris Ahlstrom
% \date        2015-08-31
% \update      2016-05-20
% \version     $Revision$
% \license     $XPC_GPL_LICENSE$
%
%     Provides the References section of the Sequencer64 manual. Rather
%     than use the bibtex package, our small set of references uses a
%     simpler method.
%
%-------------------------------------------------------------------------------

\section{References}
\label{sec:seq64_references}

   The \textsl{Yoshimi} seq24 reference list.

\begin{thebibliography}{99}

   \bibitem{alsa}
   ALSA team
   \emph{Advanced Linux Sound Architecture (ALSA) project homepage}
   \url{http://www.alsa-project.org/}
   ALSA tools through version 1.0.29.
   2015

   \bibitem{amsynth}
   amSynth team, Nick Dowell
   \emph{amSynth and Demos with Calf Effects.}
   \url{http://amsynth.com/amsynth.html}
   Includes links to demos and the source code.
   2015.

   \bibitem{bristol}
   Bristol team Nick Copeland
   \emph{Bristol: A Vintage Synthesizer Emulator}
   \url{http://www.linuxsynths.com/BristolPatchesDemos/bristol.html}
   2014.

   \bibitem{fluidsynth}
   FluidSynth team
   \emph{FluidSynth: A SoundFont Synthesizer}
   \url{http://www.fluidsynth.org/}
   2014.

   \bibitem{combine}
   Jay Capela Music
   \emph{"Combine": A Seq24 Demonstration}
   \url{https://www.youtube.com/watch?v=fUiXbVT0bJQ}
   2010.

   \bibitem{jack}
   JACK team
   \emph{JACK Audio Connection Kit}
   \url{http://jackaudio.org/}
   2015.

   \bibitem{linuxsynths}
   LinuxSynths team, briandc@linuxsynths.com
   \emph{A Sonic Palette on the Linux Platform.}
   \url{http://www.linuxsynths.com/}
   2015.

   \bibitem{ljtutorial}
   Dave Phillips
   \emph{At the Sounding Edge: Introducing seq24.}
   \url{http://www.linuxjournal.com/article/8304}
   Linux Journal, May 12, 2005.

   \bibitem{midicvt}
   Chris Ahlstrom
   \emph{Extension of midicomp/midi2text to convert between MIDI and ASCII
      text format.}
   \url{https://github.com/ahlstromcj/midicvt}
   2015-2016.

   \bibitem{midicontrol}
   linuxaudio.org
   \emph{seq24: toggle sequences with a MIDI controller}
   \url{http://wiki.linuxaudio.org/wiki/seq24togglemiditutorial}
   2013.

   \bibitem{midicontroltable}
   midi.org
   \emph{Summary of MIDI Messages}
   \url{https://www.midi.org/specifications/item/table-1-summary-of-midi-message#2}
   Year unknown.

   \bibitem{portmidi}
   PortMedia team
   \emph{Platform Independent Library for MIDI I/O}
   \url{http://portmedia.sourceforge.net/portmidi/}
   2010.

   \bibitem{seq24}
   Seq24 Team.
   \emph{The home site for the Sequencer64 looping sequencer.}
   \url{http://www.filter24.org/seq24/download.html}
   2010.

   \bibitem{seq24demo1}
   pneumanlsd.
   \emph{Linux audio demo: Live sequencing with seq24}
   \url{https://www.youtube.com/watch?v=f8zLV0vlSpY}
   2010.

   \bibitem{seq24demo2}
   synthWF.
   \emph{Misty Corridor - Seq24 (with QSynth)}
   \url{https://www.youtube.com/watch?v=RH99zHvffGQ}
   2012.

   \bibitem{seq24part1}
   pneumanlsd.
   \emph{Linux music tutorial: seq24, part 1}
   \url{https://www.youtube.com/watch?v=J2WDHS1wYeM}
   2010.
   
   \bibitem{seq24part2}
   pneumanlsd.
   \emph{Linux music tutorial: seq24, part 2}
   \url{https://www.youtube.com/watch?v=i3Vpi3oxdqk}
   2010.

   \bibitem{seq24launchpad}
   Seq24 Team.
   \emph{The home site for the Sequencer64 looping sequencer.}
   \url{https://launchpad.net/seq24}
   2016.

   \bibitem{sequencer64}
   Chris Ahlstrom.
   \emph{A continuation of the Sequencer64 project as "Sequencer64".}
   \url{https://github.com/ahlstromcj/sequencer64/}
   2016.

   \bibitem{sequencer64doc}
   Chris Ahlstrom.
   \emph{The Sequencer64 User Manual.}
   \url{https://github.com/ahlstromcj/sequencer64-doc/}
   2016.

   \bibitem{subatomicglue}
   Kevin at subatomicglue.com
   \emph{Subatomic Mods for Seq24 Win32}
   \url{http://www.subatomicglue.com/seq24/}
   2010.

   \bibitem{timidity}
   Timidity++ Team.
   \emph{Download site for Timidity++ source code.}
   \url{http://sourceforge.net/projects/timidity/}
   2015.

   \bibitem{wootangent1}
   Author's name.
   \emph{Sequencer64 Tutorial Video, Part 1.}
   \url{http://wootangent.net/2010/10/linux-music-tutorial-seq24-part-1/}
   2010.

   \bibitem{wootangent2}
   Author's name.
   \emph{Sequencer64 Tutorial Video, Part 2.}
   \url{http://wootangent.net/2010/10/linux-music-tutorial-seq24-part-2/}
   2010.

   \bibitem{yoshimi}
   Yoshimi team \url{abrolag@users.sourceforge.net}
   \emph{The download site for the Yoshimi software synthesizer.}
   \url{http://yoshimi.sourceforge.net/}
   2015.

   \bibitem{yoshimi2}
   Yoshimi team
   \emph{The alternate location for the Yoshimi source-code.}
   \url{https://github.com/abrolag/yoshimi/}
   2015.

   \bibitem{yoshimidoc}
   Chris Ahlstrom
   \emph{A Yoshimi User Manual.}
   \url{https://github.com/ahlstromcj/yoshimi-doc/}
   2015.

   \bibitem{yoshimicook}
   Chris Ahlstrom
   \emph{A Yoshimi Cookbook.}
   \url{https://github.com/ahlstromcj/yoshimi-cookbook/}
   2015.

   \bibitem{zynaddsubfx}
   Mark McCurry, Paul Nasca (ZynAddSubFX team)
   \emph{The download site for the ZynAddSubFX software synthesizer.}
   \url{http://zynaddsubfx.sourceforge.net/}
   2015.

\end{thebibliography}

%-------------------------------------------------------------------------------
% vim: ts=3 sw=3 et ft=tex
%-------------------------------------------------------------------------------
