%-------------------------------------------------------------------------------
% seq64_concepts
%-------------------------------------------------------------------------------
%
% \file        seq64_concepts.tex
% \library     Documents
% \author      Chris Ahlstrom
% \date        2015-11-01
% \update      2018-10-05
% \version     $Revision$
% \license     $XPC_GPL_LICENSE$
%
%     Provides some concepts and terms needed to understand Sequencer64.
%
%-------------------------------------------------------------------------------

\section{Concepts}
\label{sec:concepts}

   The \textsl{Sequencer64} program is basically a loop-playing machine with a 
   fairly simple interface.  Before we describe this interface, it is useful
   to present some concepts and definitions of terms as
   they are used in \textsl{Sequencer64}.  Various terms have been used over
   the years to mean the same thing (e.g. "sequence", "pattern", "loop", and
   "slot"), so it is good to clarify the terminology.

\subsection{Concepts / Terms}
\label{subsec:concepts_terms}

   This section doesn't provide comprehensive coverage of terms.  It
   covers terms that puzzled the author at first or that are
   necessary to understand the \textsl{Sequencer64} program.

\subsubsection{Concepts / Terms / armed}
\label{subsubsec:concepts_terms_armed}

   \index{armed}
   An armed sequence is a sequence
   (see \sectionref{subsubsec:concepts_terms_sequence})
   that will be heard.  "Armed" is the opposite
   of "muted".  Performing an \textsl{arm} operation in \textsl{Sequencer64}
   means clicking on an "unarmed" sequence in the patterns panel (the main
   window of \textsl{Sequencer64}).  An unarmed sequence will not be heard, and
   it has a white background.  When the sequence is \textsl{armed}, it will be
   heard, and it has a black background.
   A sequence can be armed or unarmed in three ways:

   \begin{itemize}
      \item Clicking or Shift-clicking on a sequence/pattern box.
      \item Pressing the hot-key for that sequence/pattern box.
      \item Opening up the Song Editor and starting playback; the
            sequences arm/unarm depending on the layout of the
            sequences and triggers in the piano roll of the Song Editor.
   \end{itemize}

\subsubsection{Concepts / Terms / bank}
\label{subsubsec:concepts_terms_bank}

   \index{bank}
   See \sectionref{subsubsec:concepts_terms_screen_set}.
   This term is \textsl{Kepler34}'s name for "screen set".

\subsubsection{Concepts / Terms / buss (bus)}
\label{subsubsec:concepts_terms_buss}

   \index{bus}
   \index{buss}
   A \textsl{buss} (also spelled "bus" these days;
   \url{https://en.wikipedia.org/wiki/Busbar}) is an entity onto which
   MIDI events can be placed, in order to be heard or to affect the
   playback.
   A \textsl{buss} is just another name for port.
   See \sectionref{subsubsec:concepts_terms_port}.

\subsubsection{Concepts / Terms / export}
\label{subsubsec:concepts_terms_export}

   \index{export}
   A \textsl{export} in \textsl{Sequencer64} is a way of writing a
   song-performance to a more standard MIDI file, so that it can be played
   by other sequencers.  An export collects all of the unmuted tracks that have
   performance information (triggers) associated with them, and creates one
   larger trigger for each track, repeating the events as indicated by the
   original performance.

\subsubsection{Concepts / Terms / group}
\label{subsubsec:concepts_terms_group}

   \index{group}
   A \textsl{group} in \textsl{Sequencer64} is one of up to 32
   previously-defined mute/unmute patterns in the active screen set.
   A group is a set of patterns, in the current screen-set,
   that can arm (unmute) their playing state
   together.  Every group contains all 32 sequences in the active screen
   set.  This concept is similar to mute/unmute groups in hardware
   sequencers.
   \index{mute-group}
   Also known as a "mute-group".

\subsubsection{Concepts / Terms / loop}
\label{subsubsec:concepts_terms_loop}

   \index{loop}
   \textsl{Loop}
   is a synonym for \textsl{pattern} or \textsl{sequence}, when used
   in existing \textsl{Seq24} documentation.
   Each loop is represented by a box (pattern slot) in the Pattern (main)
   Window.

\subsubsection{Concepts / Terms / measures ruler}
\label{subsubsec:concepts_terms_measures_ruler}

   \index{measures ruler}
   The \textsl{measures ruler} is the bar at the top of the Pattern Editor
   and Song Editor windows that shows the numbering of the measures in the
   song.  Left, right, or end markers can be dropped on this ruler to set
   durations to be played, looped, expanded, or collapsed.

   Note:
   \index{bar indicator}
   The original \textsl{Seq24} documentation calls this item the
   \textsl{bar indicator}.

\subsubsection{Concepts / Terms / event strip}
\label{subsubsec:concepts_terms_event_strip}

   \index{event strip}
   The \textsl{event strip} is the bar at the bottom of the Pattern Editor
   window that shows the location of events in the pattern.
   For Note On and Note Off events, it is shown in gray to warn the user to be
   careful in moving these events.

\subsubsection{Concepts / Terms / muted}
\label{subsubsec:concepts_terms_muted}

   \index{muted}
   The opposite of \sectionref{subsubsec:concepts_terms_armed}.

\subsubsection{Concepts / Terms / MIDI clock}
\label{subsubsec:concepts_terms_midi_clock}

   \textsl{MIDI clock} is
   \index{midi clock}
   a MIDI timing reference signal used to synchronize pieces of equipment
   together. MIDI clock runs at a rate of 24 ppqn (pulses per quarter note).
   This means that the actual speed of the MIDI clock varies with the tempo
   of the clock generator (as contrasted with time code, which runs at a
   constant rate). \textsl{Sequencer64} emits MIDI clock events, but does not
   (yet) follow MIDI clock.

\subsubsection{Concepts / Terms / pattern}
\label{subsubsec:concepts_terms_pattern}

   A \textsl{Sequencer64} \textsl{pattern}
   \index{pattern}
   (also called a "sequence" or "loop")
   is a short unit of melody or rhythm in \textsl{Sequencer64},
   extending for a small number of measures (in most cases).
   Each pattern is represented by a box in the Patterns window.

   Each pattern is editable on its own.  All patterns can be layed out in
   a particular arrangement to generate a more complex song.

   \textsl{pattern} is a synonym for \textsl{loop} or \textsl{sequence}.
   It is our preferred term.

\subsubsection{Concepts / Terms / performance}
\label{subsubsec:concepts_terms_performance}

   In the jargon of \textsl{Sequencer64}, a
   \index{performance}
   \textsl{performance} is an organized collection of patterns.
   This layout of patterns is created using the Song Editor, sometimes
   called the "performance editor".
   This window controls the song playback in "Song Mode".
   The playback of each track is controlled by a set of triggers created for
   that track.

\subsubsection{Concepts / Terms / port}
\label{subsubsec:concepts_terms_port}

   \index{port}
   A \textsl{port} is just another name for buss.
   See \sectionref{subsubsec:concepts_terms_buss}.
   Each port can support 16 MIDI channels.

\subsubsection{Concepts / Terms / pulses per quarter note}
\label{subsubsec:concepts_terms_pulses}

   \index{pulses}
   The concept of "pulses per quarter note", or PPQN, is very important for
   MIDI timing.  To make it a bit more confusing, sometimes these pulses are
   referred to as "ticks", "clocks", and "divisions".
   To make it even more confusing, there are separate timing concepts to
   understand, such as "tempo", "beats per measure", "beats per minute",
   "MIDI clocks", and more.

   While a full description of all these terms, and how they are calculated, is
   beyond the scope of this document, we will try to clarify the discussion
   when such confusion could be an issue.

\subsubsection{Concepts / Terms / queue mode}
\label{subsubsec:concepts_terms_queue_mode}

   To "queue" a pattern means to ready it for playback on the next repeat of
   a pattern.  A pattern can be armed immediately, or it can be queued to
   play back the next time the pattern restarts.
   Pattern toggles occur at the end of
   the pattern, rather than being set immediately.

   A set of queued patterns can be temporarily stored, so that a different
   set of playbacks can occur, before the original set of playbacks is
   restored.

   \index{keep queue}
   \index{queue!keep}
   The "keep queue" functionality allows the queue to be held without
   holding down a button the whole time.  Once this key is pressed,
   then the hot-keys for any pattern can be pressed, over and over,
   to queue each pattern.

\subsubsection{Concepts / Terms / replace}
\label{subsubsec:concepts_terms_replace}

   Replacement is a form of muting/unmuting.  When the "replace" key is
   pressed while click a sequence, that sequence is unmuted, and all of the
   other sequences are muted.

\subsubsection{Concepts / Terms / screen set}
\label{subsubsec:concepts_terms_screen_set}

   \index{screen set}
   The \textsl{screen set}
   is a set of patterns that fit within the 8x4 grid of loops/patterns in the
   Patterns panel.
   \textsl{Sequencer64} supports multiple screens sets, up to 32 of them,
   and a name can be given to each for clarity.
   The Gtkmm-2.4 version of \textsl{Sequencer64}
   supports an 8x8 grid and 64 patterns per screen set.

\subsubsection{Concepts / Terms / bank}
\label{subsubsec:concepts_terms_bank}

   \index{bank}
   The term \textsl{bank} comes from the \textsl{Kepler34} application.
   It means the same thing as \textsl{screen set}.

\subsubsection{Concepts / Terms / sequence}
\label{subsubsec:concepts_terms_sequence}

   \index{sequence}
   \textsl{Sequence} is
   another synonym for \textsl{pattern}, used in some of the \textsl{Seq24}
   documentation.  \textsl{Loop} is another synonym.
   Each sequence is represented by a box (pattern slot) in the Patterns window.

   Note that many, for other sequencer applications) use the term "sequence"
   to apply to the complete song, and not just to one track or pattern in the
   entire song.

\subsubsection{Concepts / Terms / snapshot}
\label{subsubsec:concepts_terms_snapshot}

   \index{snapshot}
   A \textsl{Sequencer64} \textsl{snapshot} is simply a briefly preserved
   state of the patterns.  One can press a snapshot key, change the state of
   the patterns for live playback, and then release the snapshot key to
   revert to the state when it was first pressed.  (One might call it a
   "revert" key, instead.)

\subsubsection{Concepts / Terms / song}
\label{subsubsec:concepts_terms_song}

   \index{song}
   A \textsl{song} is a collection of patterns in a specific temporal
   layout, as assembled via the Song Editor window.
   See \ref{subsubsec:concepts_terms_performance}.
   See \ref{subsubsec:concepts_terms_trigger}.

\subsubsection{Concepts / Terms / trigger}
\label{subsubsec:concepts_terms_trigger}

   \index{trigger}
   A \textsl{trigger} is a small data structure that indicates when a sequence
   should be played, and how much of the sequence (including repeats) should be
   played.  A song performance consists of a number of sequences, each
   triggered in ways that the musician can lay out.

\subsection{Concepts / Sound Subsystems}
\label{subsec:concepts_sound_subsystems}

\subsubsection{Concepts / Sound Subsystems / ALSA}
\label{subsubsec:concepts_sound_alsa}

   \textsl{ALSA} is a sound and MIDI system for Linux, with components built
   into the Linux kernel. It is the main subsystem used by
   \textsl{Sequencer64}.  The name of the library used to build
   \textsl{ALSA} projects is \texttt{libasound}.
   See reference \cite{alsa}.

\subsubsection{Concepts / Sound Subsystems / PortMIDI}
\label{subsubsec:concepts_sound_portmidi}

   \textsl{PortMIDI} is a cross-platform API (applications programming
   interface) for MIDI.  It seems to be used in the "portmidi" C++ modules
   included with the base source-code repository of \textsl{Seq24} available
   (for example) from Debian Linux.  See reference \cite{portmidi}
   for the PortMIDI home page.  Unfortunately, the code in the Debian
   package is not quite ready to build on Windows.  We might fix that
   someday, though Windows is not a high priority.

   The SubatomicGlue Windows port of \textsl{Seq24} (see reference
   \cite{subatomicglue}) bundles a version of the PortMIDI project with the
   source code for the port.  It also provides a complete bundle of the
   other products (e.g. gtkmm 2.4) needed to build and run the project.
   (By the way, the Windows port is built with
   MingW, which provides the GNU compilers and tools.  This is a good thing,
   as Visual Studio Community, though "free", is not "Free".)

\subsubsection{Concepts / Sound Subsystems / JACK}
\label{subsubsec:concepts_sound_jack}

   \textsl{JACK} is a cross-platform (with an emphasis on Linux)
   API and infrastructure for making it easier to connect and reroute MIDI
   and audio event between various applications and hardware ports.
   See reference \cite{jack}.

%-------------------------------------------------------------------------------
% vim: ts=3 sw=3 et ft=tex
%-------------------------------------------------------------------------------
