%-------------------------------------------------------------------------------
% seq64_midi_formats
%-------------------------------------------------------------------------------
%
% \file        seq64_midi_formats.tex
% \library     Documents
% \author      Chris Ahlstrom
% \date        2015-09-03
% \update      2015-11-10
% \version     $Revision$
% \license     $XPC_GPL_LICENSE$
%
%     Provides a discussion of the formats (legacy and new) of the last
%     track of an Seq24/Sequencer64 MIDI file.
%
%-------------------------------------------------------------------------------

\section{Proprietary Track Format and Other MIDI Notes}
\label{sec:proprietary_track_and_midi_notes}

\subsection{Legacy Proprietary Track Format}
\label{subsec:legacy_proprietary_track_format}

   Before we get to the last, proprietary track, note that the tracks that
   precede it include the SeqSpec ("sequencer-specific", sort of)
   control tags shown in \tableref{table:seqspec_items_normal_tracks}.
   These control tags are global constants in the \textsl{Seq24} source
   code, ranging from 0x24240001 to 0x24240010..

   \begin{table}[htb]
      \centering
      \caption{SeqSpec Items in Normal Tracks}
      \label{table:seqspec_items_normal_tracks}
      \begin{tabular}{l l}
         \texttt{c\_midibus}        & \texttt{24 24 00 01 00 00 00 00} \\
         \texttt{c\_midich}         & \texttt{24 24 00 02 00 00 00 00} \\
         \texttt{c\_timesig}        & \texttt{24 24 00 06 00 00 00 00} \\
         \texttt{c\_triggers\_new}  & \texttt{24 24 00 08 00 00 00 00} \\
      \end{tabular}
   \end{table}

   Note that these tags (not created by the application, and not present in
   the proprietary track, but created by other MIDI applications) are
   preceded by the standard MIDI "FF 7F length" meta-event sequence.

   The following discussion applies to the final "proprietary" track as
   saved in the legacy \textsl{Seq24} format.

   After all the counted MIDI tracks are read, \textsl{Seq24} checks for
   extra data.  If there is extra data, \textsl{Seq24} reads a long value.
   The first one encountered is a MIDI "sequencer-specific"
   (\textsl{SeqSpec}) section.  It starts with

   \begin{verbatim}
      0x24240010 == a Seq24 c\_midictrl proprietary value
   \end{verbatim}

   Getting this value first is simplified MIDI in two ways.
   First, the second does not begin with any kind of track marker.  MIDI
   requires an "MTrk" marker to start a track, though it also requires
   unknown markers to be supported.  Some applications, like
   \textsl{timidity}, handle this situation.  Others, like \textsl{midicvt},
   complain about an unexpected header marker.
   Second, normally, MIDI wants to see the triad of

   \begin{verbatim}
      status = FF, type= 7F (proprietary), length = whatever
   \end{verbatim}

   to precede proprietary data.
   Now, as shown by \tableref{table:midi_file_support_table},
   most applications accept the shortcut legacy format, but \textsl{midicvt}
   does not.

   So, as a "bug" fix, we want to be able to write and read
   this information properly in \textsl{Sequencer64}.
   We also need to be able to read legacy Seq24 MIDI files.

   Anyway, at this point, we have the \textbf{c\_midictrl} information now.
   Next, we read a long value, seqs.  It is 0.

   \begin{verbatim}
      24 24 00 10 00 00 00 00
   \end{verbatim}

   Read the next long value, 0x24240003.  This is \textbf{c\_midiclocks}.
   We get a value of 0 for "TrackLength" (now a local variable called
   "busscount"):

   \begin{verbatim}
      24 24 00 03 00 00 00 00
   \end{verbatim}

   If the buss-count was greater than 0, then for each value, we would read a
   byte value represent the bus a clock was on, and setting the clock value
   of the master MIDI buss.
   Another check for more data is made.

   \begin{verbatim}
      24 24 00 05 00 20 00 00
   \end{verbatim}

   0x24240005 is \textbf{c\_notes}.  The value screen\_sets is read (two
   bytes) and
   here is 0x20 = 32.  For each screen-set:

   \begin{verbatim}
      len = read\_short()
   \end{verbatim}

   If non-zero, each of the \texttt{len} bytes is appended as a string.
   Here, len is 0 for all 32 screensets, so the screen-set notepad is set to
   an empty string.
   Another check for more data is made.

   \begin{verbatim}
      24 24 00 07 00 00 00 78
   \end{verbatim}

   0x24240007 is \textbf{c\_bpmtag}.  The long value is read and sets the
   perform object's bpm value.  Here, it is 120 bpm.
   Another check for more data is made.

   \begin{verbatim}
      24 24 00 09 00 00 04 00
   \end{verbatim}

   0x24240009 is \textbf{c\_mutegroups}.  The long value obtained here is
   1024.  If this value is not equal to the constant
   \textbf{c\_gmute\_tracks} (1024), a warning is emitted to the console,
   but processing continues anyway, 32 x 32 long values are read to select
   the given group-mute, and then set each of its 32 group-mute-states.

   In our sample file, 32 groups are specified, but all 32 group-mute-state
   values for each are 0.

   So, to summarize the legacy proprietary track's data, ignoring the data
   itself, which is mostly 0 values, as shown in
   \tableref{table:seqspec_items_legacy_track}

   \begin{table}[htb]
      \centering
      \caption{SeqSpec Items in Legacy Proprietary Track}
      \label{table:seqspec_items_legacy_track}
      \begin{tabular}{l l}
\texttt{c\_midictrl}    & \texttt{24 24 00 10 00 00 00 00} \\
\texttt{c\_midiclocks}  & \texttt{24 24 00 03 00 00 00 00} (buss count = 0) \\
\texttt{c\_notes}       & \texttt{24 24 00 05 00 20 00 00} (screen sets = 32) \\
\texttt{c\_bpmtag}      & \texttt{24 24 00 07 00 00 00 78} (bpm = 120) \\
\texttt{c\_mutegroups}  & \texttt{24 24 00 09 00 00 04 00} (mg = 1024) \\
      \end{tabular}
   \end{table}

   The new format (again, ignoring the data) takes up a few more bytes.
   It starts with the normal track marker and size data, followed by a
   made-up track name ("Sequencer64-S"),
   as shown in \tableref{table:seqspec_items_new_track}.

   \begin{table}[htb]
      \centering
      \caption{SeqSpec Items in New Proprietary Track}
      \label{table:seqspec_items_new_track}
      \begin{tabular}{l l}
\texttt{"MTrk" etc.}   & \texttt{4d 54 72 6b 00 00 11 0d 00 ...} \\
\texttt{Track name}    & \texttt{53 65 71 75 65 6e 63 65 72 32 34 2d 53} \\
\texttt{c\_midictrl}   & \texttt{ff 7f 04 24 24 00 10 00} (???) \\
\texttt{c\_midiclocks} & \texttt{ff 7f 04 24 24 00 03 00} (buss count = 0) \\
\texttt{c\_notes}      & \texttt{ff 7f 46 24 24 00 05 00 20 00...} (screen sets = 32) \\
\texttt{c\_bpmtag}     & \texttt{ff 7f 08 24 24 00 07 00 00 00 78} (bpm = 120) \\
\texttt{c\_mutegroups} & \texttt{ff 7f a1 08 24 24 00 09 00 00 04 00...} (mg = 1024) \\
      \end{tabular}
   \end{table}

For the new format, the components of the final proprietary track size are
as shown here:

   \begin{enumber}
      \item \textbf{Delta time}.  1 byte, always 0x00.
      \item \textbf{Sequence number}.  5 bytes.  OPTIONAL.
      \item \textbf{Track name}. 3 + 10 or 3 + 15
      \item \textbf{Series of proprietary specs}:
      \begin{itemize}
         \item \textbf{Prop header}:
         \begin{itemize}
            \item If legacy format, 4 bytes.
            \item Otherwise, 2 bytes + varinum\_size(length) + 4 bytes.
            \item Length of the prop data.
         \end{itemize}
      \end{itemize}
      \item \textbf{Track End}. 3 bytes.
   \end{enumber}

\subsection{MIDI Information}
\label{subsec:midi_information}

   This section just provides some useful, basic information about MIDI
   data.

\subsubsection{MIDI Variable-Length Value}
\label{subsubsec:midi_variable_length_value}

   \index{VLV}
   A variable-length value (VLV) is a quantity that uses additional bytes
   and continuation bits to encode large numbers without confusing a MIDI
   interpreter.
   See \url{https://en.wikipedia.org/wiki/Variable-length\_quantity}.

   The length of a variable length value obviously depends on the value it
   represents.  Here is a simple list of the numbers that can be represented
   by a VLV:

   \begin{verbatim}
      1 byte:  0x00 to 0x7F
      2 bytes: 0x80 to 0x3FFF
      3 bytes: 0x4000 to 0x001FFFFF
      4 bytes: 0x200000 to 0x0FFFFFFF
   \end{verbatim}

\subsubsection{MIDI Track Chunk}
\label{subsubsec:midi_track_chunk}

   \texttt{Track chunk == MTrk + length + track\_event [+ track\_event ...]}

   \begin{itemize}
      \item \textsl{MTrk} is 4 bytes representing the literal string "MTrk".
         This marks the beginning of a track.
      \item \textsl{length} is 4 bytes the number of bytes in the track
         chunk following this number.  That is, the marker and length are
         not counted in the length value.
      \item \textsl{track\_event} denotes a sequenced track event; usually
         there are many track events in a  track.  However, some of the
         events may simply be informational, and not modify the audio
         output.
   \end{itemize}

   A track event consists of a delta-time since the last event, and one of
   three types of events.
 
   \texttt{track\_event = v\_time + midi\_event | meta\_event | sysex\_event}
 
   \begin{itemize}
      \item \textsl{v\_time} is the variable length value for elapsed time
         (delta time) from the previous event to this event.
      \item \textsl{midi\_event} is any MIDI channel message such as note-on
         or note-off.
      \item \textsl{meta\_event} is an SMF meta event.
      \item \textsl{sysex\_event} is an SMF system exclusive event.
   \end{itemize}

\subsubsection{MIDI Meta Events}
\label{subsubsec:midi_meta_events}

   Meta events are non-MIDI data of various sorts consisting of a fixed prefix,
   type indicator, a length field, and actual event data..
 
   \texttt{meta\_event = 0xFF + meta\_type + v\_length + event\_data\_bytes}

   \begin{itemize}
      \item \textsl{meta\_type} is 1 byte, expressing one of the meta event
         types shown in the table that follows this list.
      \item \textsl{v\_length} is length of meta event data, a variable
         length value.
      \item \textsl{event\_data\_bytes} is the actual event data.
   \end{itemize}

   \begin{table}
      \centering
      \caption{MIDI Meta Event Types}
      \label{table:midi_meta_event_types}
      \begin{tabular}{l l}
         Type	& Event \\
         0x00	& Sequence number \\
         0x01	& Text event \\
         0x02	& Copyright notice \\
         0x03	& Sequence or track name \\
         0x04	& Instrument name \\
         0x05	& Lyric text \\
         0x06	& Marker text \\
         0x07	& Cue point \\
         0x20	& MIDI channel prefix assignment \\
         0x2F	& End of track \\
         0x51	& Tempo setting \\
         0x54	& SMPTE offset \\
         0x58	& Time signature \\
         0x59	& Key signature \\
         0x7F	& Sequencer specific event \\
      \end{tabular}
   \end{table}

   \textsl{Timidity} reads the legacy and new formats and plays the tune.
   \textsl{Sequencer64}  saves the "b4uacuse" tune out, in both formats,
   with a "MIDI divisions" value of 192, versus its original value of 120.
   The song plays a little bit faster after this conversion.

   The \textsl{midicvt} application does not read the legacy \textsl{Seq24}
   file format.  It
   expects to see the MTrk marker.  Even if the \textsl{midicvt}
   \texttt{--ignore} option is provided,
   \textsl{midicvt} does not like the legacy \textsl{Seq24} format, and ends
   with an error message.
   However, as shown by \tableref{table:midi_file_support_table},
   most applications are more
   forgiving, and can read (or ignore) the legacy format.  The
   \textsl{gsequencer} application has some major issues in our
   installation, but it is probably our setup.  (No JACK running?)

   \begin{table}
      \centering
      \caption{Application Support for MIDI Files}
      \label{table:midi_file_support_table}
      \begin{tabular}{l l l l}
         \textbf{Application}  &
            \textbf{Legacy} &
            \textbf{New} & 
            \textbf{Original File} \\
         ardour       & TBD       & TBD       & TBD \\
         composite    & TBD       & TBD       & TBD \\
         gsequencer   & No        & No        & No \\
         lmms         & Yes       & Yes       & Yes \\
         midi2ly      & Yes       & Yes       & TBD \\
         midicvt      & No        & Yes       & Yes \\
         midish       & TBD       & TBD       & TBD \\
         muse         & TBD       & TBD       & TBD \\
         playmidi     & TBD       & TBD       & TBD \\
         pmidi        & TBD       & TBD       & TBD \\
         qtractor     & Yes       & Yes       & Yes \\
         rosegarden   & Yes       & Yes       & Yes \\
         superlooper  & TBD       & TBD       & TBD \\
         timidity     & Yes       & Yes       & Yes \\
      \end{tabular}
   \end{table}

%-------------------------------------------------------------------------------
% vim: ts=3 sw=3 et ft=tex
%-------------------------------------------------------------------------------
